partial: An R Package for Creating Partial Dependence Plots

### 2016-08-08 manuscript/greenwell.tex
minor edits

As described in the introduction, the \pkg{partial} package is useful for constructing PDPs for many types of fitted models in R. These are especially useful for visualizing the relationships discovered by complex machine learning algorithms such as a random forest. The latest stable release is available from CRAN:
\begin{example}
install.packages("partial")
\end{example}

>>>>

As described in the introduction, the \pkg{partial} package is useful for constructing PDPs for many types of fitted models in R. These are especially useful for visualizing the relationships discovered by complex machine learning algorithms such as a random forest. The latest stable release is available from \href{https://github.com/bgreenwell/partial}{CRAN}:
\begin{example}
install.packages("partial")
\end{example}
The development version is located on GitHub: \url{https://github.com/bgreenwell/partial}. Bug reports and usggestions are appreciated and should be sumbitted to \url{https://github.com/bgreenwell/partial/issues}.
